Typing in tandem: language planning in multi-sentence text production is fundamentally parallel

### 2024-10-26 report/appendix/postparam_constr.Rmd
After review update

pdodge <- position_dodge(-.5)
beta_plots <- list()
delta_plots <- list()
theta_plots <- list()
datasets <- unique(ps$ds)
size <- 2
width <- 0
linewidth <- .35
beta_label <- "Fluent interkey\nintervals"
delta_label <- "Slowdown for hesitations"
theta_label <- "Probability of hesitations"

@@

delta_plots <- map(datasets, ~filter(ps, 
                                     name == "delta", 
                                     ds == .x) %>% 
                     mutate(across(c(ds,group), ~factor(.)),
                            across(c(mean, lower, upper), ~ . /1000),
                            name = delta_label) %>% 
                     ggplot(aes(y = mean, 
                                ymin = lower, 
                                ymax = upper,
                                x = location,
                                shape = group)) +
                     geom_errorbar(width = width, 
                                   alpha = .75, 
                                   linewidth = linewidth,
                                   position = pdodge) +
                     geom_point(aes(colour = group), 
                                size = size, 
                                position = pdodge) +
                     facet_grid(~name) +
                     scale_shape_manual(values = 1:length(filter(ps, ds == .x) %>% 
                                                            pull(group) %>% 
                                                            factor())) +
                     scale_colour_colorblind() +
                     scale_y_log10(labels = scales::comma) +
                     theme(axis.title = element_blank(),
                           legend.title = element_blank()) +
                     guides(colour=guide_legend(nrow=2,byrow=TRUE),
                            shape = guide_legend(nrow=2,byrow=TRUE)))

@@

plot_param <- map(1:6, ~beta_plots[[.]] + delta_plots[[.]] + theta_plots[[.]] + labs[[.]] +
                    plot_layout(guides = "collect", widths = c(.45, 1, 1, .1)) &
                    theme(legend.position = "bottom"))

@@

plot_fin_1 <-  plot_param[[2]] / plot_param[[1]] / plot_param[[3]]
plot_fin_1 <- grid.arrange(patchworkGrob(plot_fin_1), 
                           left = "Posterior estimate with 95% PIs",
                           bottom = "Transition location")
ggsave("../figures/psplots1constr.pdf", plot_fin_1, height = 6, width = 6)

plot_fin_2 <- plot_param[[4]] / plot_param[[5]] / plot_param[[6]]
plot_fin_2 <- grid.arrange(patchworkGrob(plot_fin_2), 
                           left = "Posterior estimate with 95% PIs",
                           bottom = "Transition location")
ggsave("../figures/psplots2constr.pdf", plot_fin_2, height = 6.75, width = 6.5)
```

\begin{figure}[!htb]
\centering
\includegraphics{figures/psplots1constr.pdf}
\caption{Distribution of posterior parameter estimates with 95\% probability intervals (PI). Fluent interkey intervals are shown in msecs and the slowdown for hesitant key intervals in secs; probability of hesitations is the proportion of hesitant interkey intervals.}
\end{figure}
\newpage
\begin{figure}[!htb]
\ContinuedFloat
\captionsetup{list=off,format=cont}
\centering
\includegraphics{figures/psplots2constr.pdf}
\label{fig:fullps1}
\caption{Distribution of posterior parameter estimates with 95\% probability intervals (PI). Fluent interkey intervals are shown in msecs and the slowdown for hesitant key intervals in secs; probability of hesitations is the proportion of hesitant interkey intervals.}

>>>>

pdodge <- position_dodge(-.5)
beta_plots <- list()
delta_plots <- list()
theta_plots <- list()
datasets <- unique(ps$ds)
size <- 1.5
width <- 0
linewidth <- .35
beta_label <- "Fluent interkey\nintervals"
delta_label <- "Hesitation duration"
theta_label <- "Hesitation probability"

@@

delta_plots <- map(datasets, ~filter(ps, 
                                     name == "beta2", 
                                     ds == .x) %>% 
                     mutate(across(c(ds,group), ~factor(.)),
#                            across(c(mean, lower, upper), ~ . /1000),
                            name = delta_label) %>% 
                     ggplot(aes(y = mean, 
                                ymin = lower, 
                                ymax = upper,
                                x = location,
                                shape = group)) +
                     geom_errorbar(width = width, 
                                   alpha = .75, 
                                   linewidth = linewidth,
                                   position = pdodge) +
                     geom_point(aes(colour = group), 
                                size = size, 
                                position = pdodge) +
                     facet_grid(~name) +
                     scale_shape_manual(values = 1:length(filter(ps, ds == .x) %>% 
                                                            pull(group) %>% 
                                                            factor())) +
                     scale_colour_colorblind() +
                     scale_y_log10(labels = scales::comma) +
                     theme(axis.title = element_blank(),
                           legend.title = element_blank()) +
                     guides(colour=guide_legend(nrow=2,byrow=TRUE),
                            shape = guide_legend(nrow=2,byrow=TRUE)))

@@

plot_param <- map(1:6, ~beta_plots[[.]] + delta_plots[[.]] + theta_plots[[.]] + labs[[.]] +
                    plot_layout(guides = "collect", widths = c(.4, 1, 1, .1)) &
                    theme(legend.position = "bottom"))

@@

plot_fin_1 <-  plot_param[[2]] / plot_param[[1]] / plot_param[[3]]
plot_fin_1 <- grid.arrange(patchworkGrob(plot_fin_1), 
                           left = "Posterior estimates with 95% PIs",
                           bottom = "Transition location")
ggsave("../figures/psplots1constr.pdf", plot_fin_1, height = 6, width = 6)

plot_fin_2 <- plot_param[[4]] / plot_param[[5]] / plot_param[[6]]
plot_fin_2 <- grid.arrange(patchworkGrob(plot_fin_2), 
                           left = "Posterior estimates with 95% PIs",
                           bottom = "Transition location")
ggsave("../figures/psplots2constr.pdf", plot_fin_2, height = 6.75, width = 6.5)
```

\begin{figure}[!htb]
\centering
\includegraphics{figures/psplots1constr.pdf}
\caption{Distribution of posterior parameter estimates with 95\% probability intervals (PI). Fluent interkey intervals and hesitation durations are shown in msecs; probability of hesitations is the proportion of hesitant interkey intervals.}
\end{figure}
\newpage
\begin{figure}[!htb]
\ContinuedFloat
\captionsetup{list=off,format=cont}
\centering
\includegraphics{figures/psplots2constr.pdf}
\label{fig:fullps1}
\caption{Distribution of posterior parameter estimates with 95\% probability intervals (PI). Fluent interkey intervals and hesitation durations are shown in msecs; probability of hesitations is the proportion of hesitant interkey intervals.}

### 2024-10-26 report/appendix/prepost_constr.Rmd
After review update

```{r retesteffect, results = 'asis'}
cellmeans <- ps_plantra %>% 
  mutate(across(location, ~str_replace(., "\\n", " "))) %>% 
  pivot_wider(names_from = name, 
              values_from = c(mean, lower, upper)) %>% 
  mutate(across(ends_with("prob"), ~dezero(., 2)),
         across(c(ends_with("beta"),
                  ends_with("delta")), 
                ~as.character(scales::comma(round(.))))) %>% 
  pivot_longer(-c(location, group, ds), 
               names_to = c(".value", "param"),
               names_sep = "_") %>% 
  mutate(est = str_c(mean, " [", lower, ", ", upper,"]")) %>% 
  select(-mean:-upper, -ds) %>% 
  pivot_wider(names_from = group, values_from = est)

@@

apa_table(tmp[,-1],
          align = c("l", "r", "r", "r", "r"), 
          caption = "Mixture model estimates for post-test effect. Cell means are shown for the pre-test and post-test in msecs for the slowdown for hesitant transitions and the probability of hesitant transitions. The effect for post-test is shown on log scale (for transition durations) and logit scale for probability of hesitant transitions. 95% PIs in brackets.",
          note = "PIs are probability intervals. BF is the evidence in favour of the alternative hypothesis over the null hypothesis.",
          longtable = T,
          font_size = "footnotesize",
          stub_indents = list(
            "Hesitation duration" = 1:3,
            "Hesitation probability" = 4:6))

>>>>

```{r retesteffect, results = 'asis'}
cellmeans <- ps_plantra %>% 
  mutate(across(name, ~recode(., beta2 = "delta"))) %>% 
  mutate(across(location, ~str_replace(., "\\n", " "))) %>% 
  pivot_wider(names_from = name, 
              values_from = c(mean, lower, upper)) %>% 
  mutate(across(ends_with("prob"), ~dezero(., 2)),
         across(c(ends_with("beta"),
                  ends_with("delta")), 
                ~as.character(scales::comma(round(.))))) %>% 
  pivot_longer(-c(location, group, ds), 
               names_to = c(".value", "param"),
               names_sep = "_") %>% 
  mutate(est = str_c(mean, " [", lower, ", ", upper,"]")) %>% 
  select(-mean:-upper, -ds) %>% 
  pivot_wider(names_from = group, values_from = est)

@@

apa_table(tmp[,-1],
          align = c("l", "r", "r", "r", "r"), 
          caption = "Mixture model estimates for post-test effect. Cellmeans are shown for pre and post-test for the duration of hesitant interkey intervals in msecs and its probability. Differences are shown on the log scale for hesitation duration and on the logit scale for the hesitation probability; 95% PIs in brackets.",
          note = "PIs are probability intervals. BF is the evidence in favour of the alternative hypothesis over the null hypothesis.",
          longtable = T,
          font_size = "footnotesize",
          stub_indents = list(
            "Hesitation duration" = 1:3,
            "Hesitation probability" = 4:6))

### 2024-10-26 report/appendix/shift_constr.Rmd
After review update

# Key-combination effect (constrained mixture model)

The analysed datasets differ to the extent that keystroke intervals at before sentence location sometimes did (PLanTra, LIFT) or did not (CATO, C2L1, SPL2, GUNNEXP2) scope over the character following the shift key. In other words, the pause before sentences summed across two key intervals in the PLanTra and LIFT data, namely `_^[shift]^C` but only involved one key interval, namely `_^[shift]` for the remaining datasets. Therefore, longer or more frequent pauses at before-sentence locations compared to before-word locations can be explained without reference to linguistic edges.

<!-- Also there is a possibility that some inconsistencies in our findings can be explained on the basis of including the keystroke following shift.  -->

Therefore we compared whether the different patterns can be explain on the basis of the additional keystroke involved in before-sentence transitions. We compared the SPL2 data including and excluding the keystroke after shift. Although we modelled all transition locations, we present only before-sentence transitions below as there was, as one would expect, no difference at word locations. The results of this comparison can be found in Table \ref{tab:shiftcellmeans}.

```{r shiftcellmeans, results = 'asis'}
# cell means and data set difference
cellmeans <- ps_spl2_both %>% 
  separate(group, into = c("group", "lang"), sep = "; ") %>%
  select(-ds, -group) %>%
  mutate(across(lang, ~str_remove(., "Language: ")),
         across(location, ~str_replace(., "\\n", " "))) %>% 
  pivot_wider(names_from = name, 
              values_from = c(mean, lower, upper)) %>% 
  mutate(across(ends_with("prob"), ~dezero(., 2)),
         across(c(ends_with("beta"),
                  ends_with("delta")), 
                ~as.character(scales::comma(round(.))))) %>% 
  pivot_longer(-c(lang, location, data), 
               names_to = c(".value", "param"),
               names_sep = "_") %>% 
  mutate(est = str_c(mean, " [", lower, ", ", upper,"]")) %>% 
  select(-mean:-upper) %>% 
  pivot_wider(names_from = data, 
              values_from = est) %>% 
  mutate(across(c(location, lang), ~ifelse(param == "beta", "overall", .))) %>% 
  unique()

@@

tmp <- map_dfr(c(file1, file2), ~read_csv(.x) %>% 
                 mutate(data = .x)) %>% 
  filter(param %in% c("beta", "delta", "theta")) %>% 
  mutate(across(value, ~ifelse(param == "theta", .*-1, value))) %>% 
  mutate(across(lang, recode, "EN" = "L1", "ES" = "L2"),
         across(data, ~sub(".*/([^/]+)/[^/]+\\..*", "\\1", .))) %>% 
  pivot_wider(names_from = data, values_from = value) %>% 
  unnest(c(spl2, spl2_shift)) %>% 
  mutate(diff = spl2_shift - spl2) %>% 
  summarise(across(diff, list(mean = mean, 
                              lower = lower, 
                              upper = upper,
                              BF = BF), 
                   .names = "{.fn}"),
            .by = c(lang, location, param)) %>% 
  mutate(across(mean, ~pmap_chr(list(., lower, upper, 2), PI)),
         across(BF, ~ifelse(.>100, "> 100", as.character(round(.,2)))),
         across(param, recode, theta = "prob")) %>% 
  left_join(cellmeans) %>% 
  arrange(param, location, lang) %>% 
  filter(location %in% c("overall", "before sentence")) %>% 
  select(param, 
         Language = lang,
         `_^[shift] + C` = ends_with(" + C)"),
         `_^[shift]` = ends_with("FT])"),
         "Difference" = mean, BF)

@@

apa_table(tmp[,-1],
          align = c("l", "r", "r", "r", "r"), 
          caption = "Mixture model estimates for key transitions immediately preceding a sentence. Cell means are shown for transitions that do and do not involve the transition to the character following shift in msecs for the slowdown and the probability of hesitant transitions. The difference for including the transition duration to the character after shift is shown on log scale (for transition durations) and logit scale for probability of hesitant transitions. 95% PIs in brackets.",
          note = "PIs are probability intervals. BF is the evidence in favour of the alternative hypothesis over the null hypothesis.",
          font_size = "footnotesize",
          longtable = T,
          stub_indents = list("Fluent transitions" = 1,
                              "Hesitation duration" = 2:3,
                              "Hesitation probability" = 4:5) )

@@

The fluent transition duration and hesitation duration were not affected by whether or not the sentence-initial transition include the character following shift for neither language. However, we found strong evidence for an increased hesitation probability -- in both -- languages when the before-sentence key transition included the character following the shift key. Notably, the hesitation probability increased ceiling. It is not entirely surprised that the constrained mixture model identifies essentially all before-sentence transition as pauses: the constrained model does not distinguish between transition locations for the duration of fluent transitions. Therefore essentially all before-sentence transitions are identified as hesitation as they always include two keystrokes while all other transition location (which is the majority of the data) do not.

>>>>

```{r}
# get posterior
file <- list.files(path = "../../stanout/cato", 
                   pattern = "mogbetaco.+.csv$",
                   full.names = T)

ps <- read_csv(file) %>% filter(param %in% c("beta", "beta2", "prob"))

ps_beta <- filter(ps, param == "beta") %>% 
  select(beta = value) %>% 
  mutate(idx = 1:n())

ps_cato <- ps %>% filter(param != "beta") %>% 
  pivot_wider(names_from = param, values_from = value) %>% 
  unnest(cols = c(beta2, prob)) %>% 
  mutate(idx = 1:n(), .by = where(is.character)) %>% 
  left_join(ps_beta, by = join_by(idx)) %>% 
  mutate(across(c(beta2, beta), exp),
#         delta = beta2 - beta,
         across(location, str_replace, " ", "\n")) %>% 
  pivot_longer(c(beta, prob, beta2)) %>% 
  summarise(across(value, list(mean = mean, 
                               lower = lower, 
                               upper = upper), .names = "{.fn}"),
            .by = c(task, group, location, name)) %>% 
  mutate(group = str_c("Task: ", task, "; Group: ", group),
         ds = "CATO") %>% 
  select(-task)

file <- list.files(path = "../../stanout/c2l1", 
                   pattern = "mogbetacon.*.csv$",
                   full.names = T)

ps <- read_csv(file) %>% filter(param %in% c("beta", "beta2", "prob"))

ps_beta <- filter(ps, param == "beta") %>% 
  select(beta = value) %>% 
  mutate(idx = 1:n())

ps_c2l1 <- ps %>% filter(param != "beta") %>% 
  pivot_wider(names_from = param, values_from = value) %>% 
  unnest(cols = c(beta2, prob)) %>% 
  mutate(idx = 1:n(), .by = where(is.character)) %>% 
  left_join(ps_beta,by = join_by(idx)) %>% 
  mutate(across(c(beta2, beta), exp),
#         delta = beta2 - beta,
         across(location, str_replace, " ", "\n")) %>% 
  pivot_longer(c(beta, prob, beta2)) %>% 
  summarise(across(value, list(mean = mean, 
                               lower = lower, 
                               upper = upper), .names = "{.fn}"),
            .by = c(location, name)) %>% 
  mutate(ds = "C2L1",
         group = "1")

file <- list.files(path = "../../stanout/gunnexp2", 
                   pattern = "mogbetacon.*.csv$",
                   full.names = T)

ps <- read_csv(file) %>% filter(param %in% c("beta", "beta2", "prob"))

ps_beta <- filter(ps, param == "beta") %>% 
  select(beta = value) %>% 
  mutate(idx = 1:n())

ps_gunn <- ps %>% filter(param != "beta") %>% 
  pivot_wider(names_from = param, values_from = value) %>% 
  unnest(cols = c(beta2, prob)) %>% 
  mutate(idx = 1:n(), .by = where(is.character)) %>% 
  left_join(ps_beta, by = join_by(idx)) %>% 
  mutate(across(c(beta2, beta), exp),
#         delta = beta2 - beta,
         across(location, str_replace, " ", "\n")) %>% 
  pivot_longer(c(beta, prob, beta2)) %>%
  summarise(across(value, list(mean = mean, 
                               lower = lower, 
                               upper = upper), .names = "{.fn}"),
            .by = c(location, xn, name)) %>% 
  mutate(ds = "GE2") %>% 
  rename(group = xn)

file <- list.files(path = "../../stanout/lift", 
                   pattern = "mogbetaco.+.csv$",
                   full.names = T)

ps <- read_csv(file) %>% filter(param %in% c("beta", "beta2", "prob"))

ps_beta <- filter(ps, param == "beta") %>% 
  select(beta = value) %>% 
  mutate(idx = 1:n())

ps_lift <- ps %>% filter(param != "beta") %>% 
  mutate(across(genre, ~ifelse(is.na(genre), "Arg", .))) %>% 
  pivot_wider(names_from = param, values_from = value) %>% 
  unnest(cols = c(beta2, prob)) %>% 
  mutate(idx = 1:n(), .by = where(is.character)) %>% 
  left_join(ps_beta, by = join_by(idx)) %>% 
  mutate(across(c(beta2, beta), exp),
#         delta = beta2 - beta,
         across(location, str_replace, " ", "\n")) %>% 
  pivot_longer(c(beta, prob, beta2)) %>%
  summarise(across(value, list(mean = mean, 
                               lower = lower, 
                               upper = upper), .names = "{.fn}"),
            .by = c(genre, topic, location, name)) %>% 
  mutate(group = str_c("Topic: ", topic, "; Genre: ", genre),
         ds = "LIFT") %>% 
  select(-topic, -genre)

file <- list.files(path = "../../stanout/plantra", 
                   pattern = "mogbetaco.+.csv$",
                   full.names = T)

ps <- read_csv(file) %>% filter(param %in% c("beta", "beta2", "prob"))

ps_beta <- filter(ps, param == "beta") %>% 
  select(beta = value) %>% 
  mutate(idx = 1:n())

ps_plantra <- ps %>% filter(param != "beta") %>% 
  pivot_wider(names_from = param, values_from = value) %>% 
  unnest(cols = c(beta2, prob)) %>% 
  mutate(idx = 1:n(), .by = where(is.character)) %>% 
  left_join(ps_beta, by = join_by(idx)) %>% 
  mutate(across(c(beta2, beta), exp),
#         delta = beta2 - beta,
         across(location, str_replace, " ", "\n")) %>% 
  pivot_longer(c(beta, prob, beta2)) %>%
  summarise(across(value, list(mean = mean, 
                               lower = lower, 
                               upper = upper), .names = "{.fn}"),
            .by = c(task, location, name)) %>% 
  mutate(ds = "PLanTra") %>% 
  rename(group = task)

file1 <- list.files(path = "../../stanout/spl2", 
                    pattern = "mogbetaco.+.csv$",
                    full.names = T)

file2 <- list.files(path = "../../stanout/spl2_shift", 
                    pattern = "mogbetaco.+.csv$",
                    full.names = T)

ps <- map_dfr(c(file1, file2), ~read_csv(.) %>% 
                     mutate(data = .x)) %>% 
  mutate(across(data, ~sub(".*/([^/]+)/[^/]+\\..*", "\\1", .)),
         across(data, ~recode(., spl2 = "SPL2 (_^[shift])",
                              spl2_shift = "SPL2 (_^[shift] + C)"))) %>% 
  filter(param %in% c("beta", "delta", "prob"))

ps_beta <- filter(ps, param == "beta") %>% 
  select(beta = value, data) %>% 
  mutate(idx = 1:n(), .by = data)

ps_spl2_both <- ps %>% filter(param != "beta") %>% 
  pivot_wider(names_from = param, values_from = value) %>% 
  unnest(cols = c(delta, prob)) %>% 
  mutate(idx = 1:n(), .by = where(is.character)) %>% 
  left_join(ps_beta, by = join_by(idx, data)) %>% 
  mutate(across(lang, recode, "EN" = "L1", "ES" = "L2"),
         beta2 = beta + delta,
         across(c(beta2, beta), ~exp(.)),
#         delta = beta2 - beta,
         across(location, str_replace, " ", "\n")) %>% 
  pivot_longer(c(beta, prob, beta2)) %>%
  summarise(across(value, list(mean = mean, 
                               lower = lower, 
                               upper = upper),
                   .names = "{.fn}"),
            .by = c(lang, location, name, data)) %>% 
  mutate(ds = "SPL2",
         group = str_c("Data: ", data, "; Language: ", lang)) %>% 
  select(-lang)

ps_spl2 <- ps_spl2_both %>% filter(data == "SPL2 (_^[shift])")

# Combine all
ps <- bind_rows(ps_cato, ps_c2l1, ps_gunn, ps_lift, ps_plantra, ps_spl2)
```

# Key-combination effect

Interkey intervals at before sentence location either did (PLanTra, LIFT) scope over both the shift key and the character following the shift key or included only the first key following a the space immediately proceeding a sentence (CATO, C2L1, SPL2, GE2). In other words, the interkey interval before sentences are sum of two interkey intervals in the PLanTra and LIFT data, namely `_^[shift]^C`, where `^` represents a transition between keys, consists only of one interkey interval, namely `_^[shift]`, in the remaining datasets. Therefore, differences in hesitation patterns across datasets for transitions immediately proceeding a sentence could be explained without reference to edges of linguistic units.

Therefore we tested to what extent the inclusion of one additional interkey interval at sentence boundaries affected the hesitation results. We used the SPL2 data for this comparison and calculated intervals including and excluding the keystroke following a sentence-initial shift press. Although we modelled all transition locations, we present only before-sentence transitions as there was, as one would expect, no difference for before and within-word interkey intervals. The results of this comparison can be found in Table \ref{tab:shiftcellmeans} (only for the data from participants writing in their first language).

```{r shiftcellmeans, results = 'asis'}
# cell means and data set difference
cellmeans <- ps_spl2_both %>% 
  mutate(across(name, ~recode(., beta2 = "delta"))) %>% 
  separate(group, into = c("group", "lang"), sep = "; ") %>%
  filter(str_detect(lang, "L1")) %>% 
  select(-ds, -group, -lang) %>%
  mutate(#across(lang, ~str_remove(., "Language: ")),
         across(location, ~str_replace(., "\\n", " "))) %>% 
  pivot_wider(names_from = name, 
              values_from = c(mean, lower, upper)) %>% 
  mutate(across(ends_with("prob"), ~dezero(., 2)),
         across(c(ends_with("beta"),
                  ends_with("delta")), 
                ~as.character(scales::comma(round(.))))) %>% 
  pivot_longer(-c(location, data), 
               names_to = c(".value", "param"),
               names_sep = "_") %>% 
  mutate(est = str_c(mean, " [", lower, ", ", upper,"]")) %>% 
  select(-mean:-upper) %>% 
  pivot_wider(names_from = data, 
              values_from = est) %>% 
  mutate(across(c(location), ~ifelse(param == "beta", "overall", .))) %>% 
  unique()

@@

tmp <- map_dfr(c(file1, file2), ~read_csv(.x) %>% 
                 mutate(data = .x)) %>% 
  filter(param %in% c("beta", "delta", "theta")) %>% 
  mutate(across(value, ~ifelse(param == "theta", .*-1, value))) %>% 
  filter(lang %in% c("EN", "overall")) %>% 
  mutate(across(data, ~sub(".*/([^/]+)/[^/]+\\..*", "\\1", .))) %>% 
  pivot_wider(names_from = data, values_from = value) %>% 
  unnest(c(spl2, spl2_shift)) %>% 
  mutate(diff = spl2_shift - spl2) %>% 
  summarise(across(diff, list(mean = mean, 
                              lower = lower, 
                              upper = upper,
                              BF = BF), 
                   .names = "{.fn}"),
            .by = c(location, param)) %>% 
  mutate(across(mean, ~pmap_chr(list(., lower, upper, 2), PI)),
         across(BF, ~ifelse(.>100, "> 100", as.character(round(.,2)))),
         across(param, recode, theta = "prob")) %>% 
  left_join(cellmeans) %>% 
  filter(location %in% c("overall", "before sentence")) %>% 
  mutate(across(param, ~recode_factor(., 
                                `beta` = "Fluent interkey intervals",
                                `delta` = "Hesitation duration",
                                `prob` = "Hesitation probability",
                                .ordered = T))) %>% 
  select(`Model parameter` = param, 
         `_^[shift]^C` = ends_with(" + C)"),
         `_^[shift]` = ends_with("FT])"),
         "Difference" = mean, BF)

@@

apa_table(tmp,
          align = c("l", "l", "r", "r", "r", "r"), 
          caption = "Mixture model estimates for interkey interval immediately preceding a sentence. Cellmeans are shown for interkey intervals that do and do not include the interkey interval following a sentence-initial shift key press. Hesitation duration is shown in mseecs along with the hesitation probability. The difference due to the additional keystoke is shown fo the hesitation duration (log scale) and hesitation probability (logit scale); 95% PIs are shown in brackets.",
          note = "PIs are probability intervals. BF is the evidence in favour of the alternative hypothesis over the null hypothesis.",
          font_size = "footnotesize",
          longtable = T)

@@

The duration of fluent and hesitant interkey intervals was not affected by whether or not the sentence-initial transition include the character following the shift key. However, we found strong evidence for an increased hesitation probability when the before-sentence interkey interval included the character following the shift key. Notably, the hesitation probability approached ceiling when the interkey interval following the shift key was added. In other words, the mixture model identified almost all before-sentence transitions as being hesitant as they -- in the majority of cases -- included two keystrokes while interkey intervals for all other transition locations -- and therefore the majority of the data -- did not.
